Identifying regime transitions for water governance at the Yellow River Basin, China

### 2023-10-07 paper/main/02_methods.tex
fix(paper): :pencil2: water consumption -> water use

	First, for scarcity, $A_{i, j}$ is the total water consumption as a proportion of regional multi-year average runoff volume in year $j$ and region $i$ (in this study, four regions in the YRB, \textit{Supporting Information Section S1}):
	\begin{equation}
		A_{i, j} = \frac{WU_{i,j}}{R_{i, avg}}
	\end{equation}

>>>>

	First, for scarcity, $A_{i, j}$ is the total water use as a proportion of regional multi-year average runoff volume in year $j$ and region $i$ (in this study, four regions in the YRB, \textit{Supporting Information Section S1}):
	\begin{equation}
		A_{i, j} = \frac{WU_{i,j}}{R_{i, avg}}
	\end{equation}

### 2023-10-07 paper/response_letter/source/reviewer_1.tex
fix(paper): :pencil2: water consumption -> water use

>>>>

% 我们非常感谢你方对细节的关注和对我方术语的更正。我们已经复习了有问题的部分，并修改了术语，以确保我们的陈述准确和清晰。
\AR{} We greatly appreciate your attention to detail and the correction you provided regarding our terminology. We have reviewed the section in question and have amended the terminology to ensure precision and clarity in our presentation:

\begin{quote}
	First, for scarcity, $A_{i, j}$ is the total water use as a proportion of regional multi-year average runoff volume in year $j$ and region $i$ \dots
\end{quote}
